Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-04 draft.tex
tweak some sentences

The high-radix, low-diameter dragonfly network will be the choice of many computing facilities for building their next generation supercomputers. 
Preliminary studies show that random placement with adaptive routing should be the rule of thumb to utilize such networks for it can uniformly distribute traffic and alleviate congestion. 
However, in this paper, we made the observation that while random placement coupled with adaptive routing can load-balance the network, it can not guarantee the best performance for every single job.
We have observed that the performance improvement of communication-intensive jobs comes with the sacrifice of less intensive jobs. 
We identify this ``bully" behavior with the help of detailed network simulation and real application traces and validate the underneath causes.
We propose a hybrid job placement policy that provide either contiguous or random allocation to each application based on its communication intensity. 
With the help of the simulation, we demonstrate that this hybrid job placement policy can lead to performance improvement for less communication-intensive applications.

>>>>

The high-radix, low-diameter dragonfly network will be the choice of many computing facilities for building their next generation supercomputers. 
Preliminary studies show that random placement with adaptive routing should be the rule of thumb to utilize such networks for it can uniformly distribute traffic and alleviate congestion. 
However, in this paper, we made the observation that while random placement coupled with adaptive routing can load-balance the network, it can not guarantee the best performance for every single job.
The performance improvement of communication-intensive jobs comes with at the cost of performance degradation of less intensive jobs. 
We identify this ``bully" behavior and validate its underneath causes with the help of detailed network simulation and real application traces.
We propose a hybrid job placement policy providing either contiguous or random allocation to each application based on its communication intensity. 
Our experiment results demonstrate that this hybrid job placement policy can lead to performance improvement for less communication-intensive applications.

### 2016-04-04 intro.tex
tweak some sentences

Low-latency and high-bandwidth interconnect networks play a critical role in improving HPC system performance. 
The high-radix, low-diameter dragonfly topology can lower the extension cost of the interconnect, improve network bandwidth and reduce packet latency \cite{dally-dragonfly}, 
making it a very promising choice for building petaflop and beyond supercomputers. 
Even with such powerful networks, 
intelligent job placement is still of paramount importance to the efficient use of dragonfly connected systems. 
An ideal job placement policy should not only guarantee load balance on the network 
but also mitigate the performance degradation of each application due to interference.  
(Interference itself is inevitable on the dragonfly~\cite{bhatele2015, dskinner}.)

Recent studies suggest that random job placement coupled with adaptive routing can alleviate local congestion, eliminate hot-spots and reach load-balance for dragonfly networks~\cite{jain-sc14, bhatele-sc11, brandt2014}. These works explore the possible job placement and routing configurations that could optimize the overall network performance.
In this paper, we study the interference among concurrently running applications on dragonfly networks when different job placement and routing policies are in use. 
Our analysis focus on the performance of each application with interference in presence.

@@

Based on the aforementioned key observations, the optimal job placement policy for the workload running dragonfly system should be specific to the application communication intensity. Thus, we propose a hybrid job placement, which can assign the communication-intensive applications with random allocation and less intensive applications with contiguous allocation. Our experiment results show that hybrid job placement can mitigate the performance degradation of less communication-intensive applications while still guarantee the best performance of communication-intensive applications.
%\emph{The random placement and adaptive routing are preferable to communication-intensive jobs, whereas contiguous placement and minimal routing are in favor of less intensive jobs.} 
To the best of our knowledge, using real application traces from production systems for the study of job interference on dragonfly networks has not been reported so far. We believe the observations and new placement policy presented in this paper are valuable to the HPC community.
%We believe the observations and new placement policy presented in this paper are valuable to a number of communities including HPC computing centers, system software developers, and system administrators. 
%For example, the computing centers should take resource sharing into consideration when choosing proper configurations for building their dragonfly networks. System software developers could design better scheduling algorithms for jobs with distinct communication behavior. System administrators could make more accurate predication about system availability based on job running status under different placement and routing configurations.

>>>>

Low-latency and high-bandwidth interconnect networks play a critical role in improving HPC system performance. 
The high-radix, low-diameter dragonfly topology can lower the extension cost of the interconnect, improve network bandwidth and reduce packet latency \cite{dally-dragonfly}, 
making it a very promising choice for building petaflop and beyond supercomputers. 
Even with such powerful networks, 
intelligent job placement is still of paramount importance to the efficient use of dragonfly connected systems~\cite{bhatele2015, jain-sc14}. 
%An ideal job placement policy should not only load balance the network 
%but also guarantee the performance of every single application by minimizing the inevitable interference on the dragonfly network.

Recent studies suggest that random job placement coupled with adaptive routing can alleviate local congestion, eliminate hot-spots and reach load-balance for dragonfly networks~\cite{jain-sc14, bhatele-sc11, brandt2014}. 
These works explore the possible job placement and routing configurations that could optimize the overall network performance without scrutinizing the possible interference.
In this paper, we study the interference among concurrently running applications on dragonfly networks when different job placement and routing policies are in use. 
Our analysis focus on the performance of each application with interference in presence.

@@

Based on the aforementioned key observations, the ideal job placement policy for the workload running dragonfly system should be specific to the application communication intensity. Thus, we propose a hybrid job placement, which can assign the communication-intensive applications with random allocation and less intensive applications with contiguous allocation. Our experiment results show that hybrid job placement can mitigate the performance degradation of less communication-intensive applications while still guarantee the best performance of communication-intensive applications.
%\emph{The random placement and adaptive routing are preferable to communication-intensive jobs, whereas contiguous placement and minimal routing are in favor of less intensive jobs.} 
To the best of our knowledge, using real application traces from production systems for the study of job interference on dragonfly networks has not been reported so far. We believe the observations and new placement policy presented in this paper are valuable to the HPC community.
%We believe the observations and new placement policy presented in this paper are valuable to a number of communities including HPC computing centers, system software developers, and system administrators. 
%For example, the computing centers should take resource sharing into consideration when choosing proper configurations for building their dragonfly networks. System software developers could design better scheduling algorithms for jobs with distinct communication behavior. System administrators could make more accurate predication about system availability based on job running status under different placement and routing configurations.

### 2016-04-04 study_workload_2.tex
tweak some sentences

\emph{The application becomes the ``bully" in the workload only because it has more amount of data transfer compared with its concurrently running peers.} The ``bully" takes advantage of the network resource belonging to other applications when network sharing is enabled by random placement and adaptive routing policy.

>>>>

\emph{The application becomes the ``bully" only because it has more amount of data transfer compared with its concurrently running peers.} The ``bully" takes advantage of the network resource belonging to other applications when network sharing is enabled by random placement and adaptive routing policy.
